### 2022-02-07 src/text/2-package-subsections/makers.tex
Add reference to Berge07

Because the background models suffer from strong uncertainties it is required to correct
them from the data themselves. Several techniques are commonly used in gamma-ray astronomy
such as field-of-view background normalization or background measurement in reflected regions 
regions, see~\cite{test}. Specific {\tt Makers} such as the {\tt FoVBackgroundMaker} or the
{\tt ReflectedRegionsBackgroundMaker} are in charge of this step.

>>>>

Because the background models suffer from strong uncertainties it is required to correct
them from the data themselves. Several techniques are commonly used in gamma-ray astronomy
such as field-of-view background normalization or background measurement in reflected regions 
regions, see~\cite{Berge07}. Specific {\tt Makers} such as the {\tt FoVBackgroundMaker} or the
{\tt ReflectedRegionsBackgroundMaker} are in charge of this step.
